---
title: "Introduction to PakCoronaData: Pakistan COVID-19 Data"
author: "Muhammad Yaseen^1^"
date: "`r Sys.Date()`"
geometry: margin=3cm
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  pdf_document:
    dev: cairo_pdf
    fig_caption: yes
    number_sections: yes
    toc: yes  
documentclass: article
header-includes:
- \usepackage{fancyhdr}
- \usepackage{wrapfig}
- \usepackage{float}
- \pagestyle{fancy}
- \fancyfoot[C]{\thepage}
- \usepackage{hyperref}
- \hypersetup{colorlinks=true}
- \hypersetup{linktoc=all}
- \hypersetup{linkcolor=blue}
- \usepackage{pdflscape}
- \usepackage{booktabs}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \renewcommand\thesection{\arabic{section}}
link-citations: yes
csl: frontiers.csl
resource_files:
- vignettes/rbase.png
- vignettes/rstudio.png
- vignettes/rstudio panes.png
vignette: |
  %\VignetteIndexEntry{IntroPakCoronaData}
  %\usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")

r = getOption("repos")
r["CRAN"] = "https://cran.rstudio.com/"
#r["CRAN"] = "https://cloud.r-project.org/"
#r["CRAN"] = "https://ftp.iitm.ac.in/cran/"
options(repos = r)
```

```{r, results='asis', echo=FALSE}
switch(out_type,
    html = {cat("
  <p> 1. Department of Mathematics and Statistics, University of Agriculture Faisalabad, Faisalabad-Pakistan  (myaseen208@gmail.com).</p>
              ")},
    latex = cat("\\begin{center}
1. Department of Mathematics and Statistics, University of Agriculture Faisalabad, Faisalabad-Pakistan  (myaseen208@gmail.com).

\\end{center}" )
)
```

\begin{center}
\vspace{6pt}
\hrule
\end{center}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "",
                      fig.cap = "")
```

```{r echo = FALSE, message=FALSE}
library(PakCoronaData)
```

# Introduction

The `R` package `PakCoronaData` provides data set for exploration of Pakistan Demographic and Health Survey (PDHS) data [http://nips.org.pk/Home.htm](http://nips.org.pk/Home.htm). The 2017-18 Pakistan Demographic and Health Survey (PDHS) is designed to provide data for monitoring the health situation in Pakistan. The 2017-18 PDHS is the 4th DHS survey conducted in Pakistan since 1990-91. It provides reliable estimates at the national level, for urban and rural areas, and for 4 regions and 4 provinces. The national total for indicators excludes Azad Jammu and Kashmir and Gilgit Baltistan.